Spatial and temporal variability in economic availability of residual biomass from timber harvest in west-central Alberta, Canada (1990--2015)

### 2022-11-18 analysis/ms_november/hrs_2022-11-07_figs.Rmd
2022-11-18

---
title: Spatial and temporal variability in economic availability of residual biomass from timber harvest in west-central Alberta, Canada (1990--2015)
subtitle: 'Tables and Figures'
author:
  - name: Glen W. Armstrong
    institute: rr
    correspondence: 'yes' 
    email: gwa@ualberta.ca
  - name: Jay A. Anderson
    email: jaya@ualberta.ca
    institute: rees
  - name: Alex W. McPhee
    email: awmcphee@ualberta.ca
    institute: rees
institute:
   - rr: Department of Renewable Resources, University of Alberta, Edmonton AB  T6G 2H1, Canada
   - rees: Department of Resource Economics and Environmental Sociology, University of Alberta, Edmonton AB  T6G 2H1, Canada
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  pdf_document:
   includes:
     in_header: preamble.tex 
   number_sections: yes
   latex_engine: xelatex
   keep_tex: yes
   pandoc_args:
     - --lua-filter=scholarly-metadata.lua
     - --lua-filter=author-info-blocks.lua
#   bookdown::pdf_document2: default
#   html_document:
#     number_sections: yes
#     df_print: paged
#     pandoc_args:
#     - --lua-filter=scholarly-metadata.lua
#     - --lua-filter=author-info-blocks.lua
#   word_document:
#     number_sections: yes
#     pandoc_args:
#     - --lua-filter=scholarly-metadata.lua
#     - --lua-filter=author-info-blocks.lua
#   bookdown::html_document2: default
# header-includes:

>>>>

---
title: Spatial and temporal variability in economic availability of residual biomass from timber harvest in west-central Alberta, Canada (1990--2015)
subtitle: 'Tables and Figures'
author:
  - name: Glen W. Armstrong
    institute: rr
    correspondence: 'yes' 
    email: gwa@ualberta.ca
  - name: Jay A. Anderson
    email: jaya@ualberta.ca
    institute: rees
  - name: Alex W. McPhee
    email: awmcphee@ualberta.ca
    institute: rees
  - name: M.K. Luckert
    email: mluckert@ualberta.ca
    institute: rees
institute:
   - rr: Department of Renewable Resources, University of Alberta, Edmonton AB  T6G 2H1, Canada
   - rees: Department of Resource Economics and Environmental Sociology, University of Alberta, Edmonton AB  T6G 2H1, Canada
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  pdf_document:
   includes:
     in_header: preamble.tex 
   number_sections: yes
   latex_engine: xelatex
   keep_tex: yes
   pandoc_args:
     - --lua-filter=scholarly-metadata.lua
     - --lua-filter=author-info-blocks.lua
#   bookdown::pdf_document2: default
#   html_document:
#     number_sections: yes
#     df_print: paged
#     pandoc_args:
#     - --lua-filter=scholarly-metadata.lua
#     - --lua-filter=author-info-blocks.lua
#   word_document:
#     number_sections: yes
#     pandoc_args:
#     - --lua-filter=scholarly-metadata.lua
#     - --lua-filter=author-info-blocks.lua
#   bookdown::html_document2: default
# header-includes:
